Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-17 manuscript.Rmd
table

>>>>

#Bins
pt2corr_with_outliers <- map_dfc(agree_bins, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree_bins, ~ .x %>% filter(file != "107/3", file != "104/1") %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

group_agree_cor <- cor_test(agree_bins$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree_bins$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree_bins$group %>% filter(file != "107/3", file != "104/1") %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree_bins$split %>% filter(file != "107/3", file != "104/1") %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5)

### 2023-02-17 manuscript.tex
pt2 correlation table
overall row
table

>>>>

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:pt2overalltable}}

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Held & -0.02 & 0.16 & 0.59 & 0.65\\
Prone & 0.97 & 0.83 & 0.97 & 0.82\\
Sitting & 0.72 & 0.93 & 0.75 & 0.98\\
Supine & 0.84 & 0.93 & 0.87 & 0.97\\
Upright & 0.84 & 0.93 & 0.99 & 0.94\\ \midrule
Overall & 0.79 & 0.90 & 0.89 & 0.96\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-3}}

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Held & 0.45 & 0.44 & 0.59 & 0.57\\
Prone & 0.96 & 0.81 & 0.96 & 0.81\\
Sitting & 0.72 & 0.93 & 0.73 & 0.94\\
Supine & 0.75 & 0.93 & 0.76 & 0.94\\
Upright & 0.93 & 0.95 & 0.98 & 0.96\\ \midrule
Overall & 0.80 & 0.92 & 0.81 & 0.93\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}
